Pipeline Performance Figure Generation

### 2023-05-26 TestingPipeline/Scripts/paper_figure_generation.Rmd
Updated overarching heatmap.

@@

ann_colors = list(
  tnv = c("black", pal(6)[1]),
  tv = c("black", pal(6)[3]),
  dvf = c("black", pal(6)[2]),
  vb = c("black", pal(6)[4]),
  vs = c("black", pal(6)[5]),
  vs2 = c("black", pal(6)[6]),
  score = c("archaea"=pal(6)[1], "bacteria"=pal(6)[2], "fungi"=pal(6)[3],
              "plasmid"=pal(6)[4], "protist"=pal(6)[5], "virus"=pal(6)[6])
)

@@

pheatmap::pheatmap(t(viral_scores_1),
                  annotation_col = ann_row,
                  annotation_row = ann_col,
                  annotation_colors = ann_colors,
                  #border_color = "black",
                  color = c(rev(RColorBrewer::brewer.pal(3,"Oranges")),
                            RColorBrewer::brewer.pal(5,"Purples") 
                            ),
                  show_rownames = F,
                  show_colnames = F,
                  annotation_legend = F,
                  cluster_rows = F,
                  cluster_cols = F,
                  cellheight=3,
                  filename = "../IntermediaryFiles/pheatmap_virus_set_1_viral_scores.png"
                  )
```

>>>>

ggplot(accuracy_scores, aes(x=toolcombo, y=MCC, 
                                  color=numrules, fill=numrules)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=20),
  ) +
  xlab("Tool Combination (tv, DVF, tnv, VB, VS, VS2)") +
  ylab("MCC") +
  scale_fill_manual(name="Number of Rule Sets",
                     values = alpha(rev(viridis(6)), 0.5)) +
  scale_color_manual(name="Number of Rule Sets",
                     values = alpha(rev(viridis(6)), 1))

@@

ann_colors = list(
  tnv = c("black", pal(6)[1]),
  tv = c("black", pal(6)[3]),
  dvf = c("black", pal(6)[2]),
  vb = c("black", pal(6)[4]),
  vs = c("black", pal(6)[5]),
  vs2 = c("black", pal(6)[6]),
  score = c("archaea"=pal2(20)[13], "bacteria"=pal2(20)[9], "fungi"=pal2(20)[20],
              "plasmid"=pal2(20)[19], "protist"=pal2(20)[5], "virus"=pal2(20)[17])
)

@@

viral_scores_1 <- floor(viral_scores_1)

seq_scores <- rowSums(viral_scores_1)

seq_type <- table(viruses_1$seqtype)[c(6,2,1,4,5,3)]
seq_type <- cumsum(seq_type)

sub_seq_scores <- seq_scores[1:seq_type[1]]
order_seq_scores_virus <- names(sub_seq_scores)[order(sub_seq_scores)]

sub_seq_scores <- seq_scores[seq_type[1]:seq_type[2]]
order_seq_scores_bacteria <- names(sub_seq_scores)[order(sub_seq_scores)]

sub_seq_scores <- seq_scores[seq_type[2]:seq_type[3]]
order_seq_scores_archaea <- names(sub_seq_scores)[order(sub_seq_scores)]

sub_seq_scores <- seq_scores[seq_type[3]:seq_type[4]]
order_seq_scores_plasmid <- names(sub_seq_scores)[order(sub_seq_scores)]

sub_seq_scores <- seq_scores[seq_type[4]:seq_type[5]]
order_seq_scores_protist <- names(sub_seq_scores)[order(sub_seq_scores)]

sub_seq_scores <- seq_scores[seq_type[5]:seq_type[6]]
order_seq_scores_fungi <- names(sub_seq_scores)[order(sub_seq_scores)]

viral_scores_1 <- viral_scores_1[c(order_seq_scores_virus, 
                                   order_seq_scores_bacteria,
                                   order_seq_scores_archaea,
                                   order_seq_scores_plasmid,
                                   order_seq_scores_protist,
                                   order_seq_scores_fungi),]

pheatmap::pheatmap(t(viral_scores_1),
                  annotation_col = ann_row,
                  annotation_row = ann_col,
                  annotation_colors = ann_colors,
                  #border_color = "black",
                  color = c(rev(RColorBrewer::brewer.pal(9,"Oranges")[4:7]),
                            RColorBrewer::brewer.pal(9,"Purples")[4:9] 
                            ),
                  show_rownames = F,
                  show_colnames = F,
                  annotation_legend = F,
                  cluster_rows = F,
                  cluster_cols = F,
                  cellheight=3,
                  gaps_col = c(seq_type[1], seq_type[2], seq_type[3], seq_type[4], seq_type[5]),
                  legend_breaks=c(-3:5),
                  legend_labels=c(-3:5),
                  filename = "../IntermediaryFiles/pheatmap_virus_set_1_viral_scores.png"
                  )
```
